---
title: "RGL Perspective Plots"
author: "Paul Lewis"
date: "2024-07-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

Plot of simulated combinations of theta and lambda

```{r}
halftheta = c(__HALFTHETAVECTOR__)
T = c(__TVECTOR__)
numdeep = c(__NUMDEEP__)
maxdeep = c(__MAXDEEP__)
nspecies = __NSPECIES__
smcmean   <- c(__SMCRFMEANS__)

plot(halftheta, T, type="p", pch=19, main="Simulation conditions", xlab="theta/2", ylab="T")
```
Set colors for plots

```{r}
bgcolor <- "cornsilk"
planecolor <- "ghostwhite"
surfcolor <- "red"
```

Set up values used for the x-axis and y-axis of the grid

```{r}
halftheta_vals <- unique(halftheta)
cat("halftheta_vals:\n")
halftheta_vals
ncols <- length(halftheta_vals)

T_vals <- unique(T)
cat("T_vals:\n")
T_vals
nrows <- length(T_vals)
```

Plot new info content.

```{r}
info <- c(__SMC_INFO__)
infodf <- data.frame(halftheta, T, info, smcmean)
proportiondeep <- numdeep/maxdeep
```

Plot old info content.

```{r}
old_info <- c(__SMC_OLD_INFO__)
old_infodf <- data.frame(halftheta, T, old_info, smcmean)
```

Contour plot new info

```{r}
v <- ggplot(infodf, aes(halftheta, T, z = info))
v + geom_contour_filled(breaks=c(__CONTOUR_BREAKS__)) + labs(x=expression(theta/2))
```

Contour plot old info

```{r}
v <- ggplot(old_infodf, aes(halftheta, T, z = old_info))
v + geom_contour_filled(breaks=c(__CONTOUR_BREAKS__)) + labs(x=expression(theta/2))
```

Contour plot showing number of deep coalescences

```{r}
v <- ggplot(infodf, aes(halftheta, T, z = proportiondeep))
v + geom_contour_filled(breaks=c(0.0,0.2,0.4,0.6,0.8,1.0)) + labs(x=expression(theta/2))
```

# PLot RF distance vs info with points colored by ngenes
```{r}
ngenes   <- c(__NGENES__)

v <- ggplot(infodf, aes(info, smcmean, z = ngenes, color = ngenes)) + geom_jitter() +
  scale_color_gradient(low="blue", high="green")
v
```

# PLot RF distance vs info with points colored by theta/2
```{r}
v <- ggplot(infodf, aes(info, smcmean, z = halftheta, color = halftheta)) + geom_jitter() +
  scale_color_gradient(low="blue", high="green")
v
```

# PLot RF distance vs info with points colored by T
```{r}
v <- ggplot(infodf, aes(info, smcmean, z = T, color = T)) + geom_jitter() +
  scale_color_gradient(low="blue", high="green")
v
```
