---
title: "RGL Perspective Plots"
author: "Paul Lewis"
date: "2024-07-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rgl)
library(ggplot2)
```

Plot of simulated combinations of theta and lambda

```{r}
theta = c(__THETAVECTOR__)
lambda = c(__LAMBDAVECTOR__)
nspecies = __NSPECIES__
plot(theta, lambda, type="p", pch=19, main="Simulation conditions", xlab="theta", ylab="lambda")
```
Set colors for plots

```{r}
bgcolor <- "cornsilk"
planecolor <- "ghostwhite"
surfcolor <- "red"
```

Set up values used for the x-axis and y-axis of the grid

```{r}
theta_vals <- unique(theta)
cat("theta_vals:\n")
theta_vals
ncols <- length(theta_vals)

lambda_vals <- unique(lambda)
cat("lambda_vals:\n")
lambda_vals
nrows <- length(lambda_vals)
```

The rf-summary.txt and kf-summary.txt files are created by crunch.py

```{r}
smcmean   <- c(__SMCRFMEANS__)
beastmean <- c(__BEASTRFMEANS__)
smcminusbeast <- c(__SMC_MINUS_BEAST_RF__)
rf <- data.frame(theta, lambda, smcmean, beastmean)
```

Contour plot SMC on top, BEAST on bottom. of zero delta RF plane

```{r include=TRUE}
# Using ggplot2
v <- ggplot(rf, aes(theta, lambda, z = smcminusbeast))
v + geom_contour_filled(breaks=c(__CONTOUR_BREAKS__))
```

```{r include=FALSE}
# Using rgl
zfunc <- function(zmat) {
  # zmat is an n X 3 matrix, with the three columns being x, y, and z coordinates
  # Calculate a vector of z values and return
  n <- dim(zmat)[1]
  cat(sprintf("\n~~> n = %d\n", n))
  for (i in 1:n) {
    cat(sprintf("%12.5f %12.5f %12.5f\n", rf$theta[i], rf$lambda[i], rf$smcminusbeast[i]))
  }
  as.vector(rf$smcminusbeast)
}

open3d()
bg3d(color=bgcolor)
#grd <- expand.grid(x=c(0, max(T_vals)), y=c(0,max(theta_vals)), z=0)
z_vals <- matrix(rep(0, nrows*ncols),nrows,ncols)
id <- persp3d(x=theta_vals, y=lambda_vals, z=z_vals, col=planecolor, polygon_offset = 1)
cat("\nlambda_vals:\n")
print(lambda_vals)
cat("\ntheta_vals:\n")
print(theta_vals)
cat("\nz_vals:\n")
print(z_vals)
filledContour3d(id, fn=zfunc, nlevels=10, replace=TRUE)
```


Plot SMC on top of zero delta RF plane, BEAST on bottom of plane

```{r include=FALSE}
open3d()
bg3d(color=bgcolor)
light3d(theta=45)
persp3d(x=T_vals, y=theta_vals, z=matrix(rf$smcmean - rf$beastmean,nrows,ncols), col=surfcolor, zlim=c(-8,8), xlab="T", ylab="theta", zlab="delta RF")

# add the plane itself
grd <- expand.grid(x=c(0, max(T_vals)), y=c(0,max(theta_vals)), z=0)
material3d(color = planecolor)
persp3d(x=unique(grd[[1]]), y=unique(grd[[2]]), z=matrix(grd[[3]],2,2), col=planecolor,add=TRUE)
```

## Save view parameters

After adjusting the plot to look the way you want, execute this chunk to save the view parameters. These view settings will be used for plotting both SMC and BEAST.

```{r include=FALSE}
# https://stackoverflow.com/questions/22257196/get-rgl-view-parameters
zoom <- par3d()$zoom
userMatrix <- par3d()$userMatrix
windowRect <- par3d()$windowRect
```

```{r include=FALSE}
# Replot SMC
open3d(zoom = zoom, userMatrix = userMatrix, windowRect=windowRect)
bg3d(color=bgcolor)
light3d(theta=45)
persp3d(x=T_vals, y=theta_vals, z=matrix(rf$smcmean - rf$beastmean,nrows,ncols), col=surfcolor, zlim=c(-8,8), xlab="T", ylab="theta", zlab="delta RF")
grd <- expand.grid(x=c(0, max(T_vals)), y=c(0,max(theta_vals)), z=0)
material3d(color = planecolor)
persp3d(x=unique(grd[[1]]), y=unique(grd[[2]]), z=matrix(grd[[3]],2,2), col=planecolor,add=TRUE)

# Save to file
rgl.snapshot("rfdiff-smc-on-top.png", fmt="png", top=TRUE)

# Plot BEAST
open3d(zoom = zoom, userMatrix = userMatrix, windowRect=windowRect)
bg3d(color=bgcolor)
light3d(theta=45)
persp3d(x=T_vals, y=theta_vals, z=matrix(rf$beastmean - rf$smcmean,nrows,ncols), col=surfcolor, zlim=c(-8,8), xlab="T", ylab="theta", zlab="delta RF")
grd <- expand.grid(x=c(0, max(T_vals)), y=c(0,max(theta_vals)), z=0)
material3d(color = planecolor)
persp3d(x=unique(grd[[1]]), y=unique(grd[[2]]), z=matrix(grd[[3]],2,2), col=planecolor,add=TRUE)

# Save to file
rgl.snapshot("rfdiff-beast-on-top.png", fmt="png", top=TRUE)
```
